Capstone Movielens Report

### 2025-12-23 reports/capstone-movielens.site/02-3.OMR-model.Rmd
Report refactoring: references to `Appendix A`.

The [piece of code] below prints a quick recap of the results:
```{r main-script@l177}
which_min_deviation <- deviation[which.min(deviation.RMSE)]
min_rmse = min(deviation.RMSE)

@@

::: {.noteblock data-latex=""}
To print the log, we use the function [print_log1](#func.print_log1) described in the [Logging Functions] section of [Appendix A](#appndx_a).
:::

>>>>

The [piece of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L177) below prints a quick recap of the results:
```{r main-script@l177}
which_min_deviation <- deviation[which.min(deviation.RMSE)]
min_rmse = min(deviation.RMSE)

@@

::: {.noteblock data-latex=""}
To print the log, we use the function [print_log1](#func.print_log1) described in the [Common Helper Functions]/[Logging Functions] section of [Appendix A](#appndx_a).
:::

### 2025-12-23 reports/capstone-movielens.site/02.4.UE-model.Rmd
Report refactoring: references to `Appendix A`.

These considerations allow us to compute a _User Mean Ratings_ using the following [piece code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L231):
```{r  main-script@l1231, eval=FALSE}
put_log("Computing Average Ratings per User (User Mean Ratings)...")
user.mean_ratings <- rowMeans(edx.mx, na.rm = TRUE)
user_ratings.n <- rowSums(!is.na(edx.mx))

@@

The following [code snippet](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L336) plots a histogram that provides a visual representation of the *User Effect* data object we have just obtained:
```{r main-script@l336}
par(cex = 0.7)
hist(edx.user_effect$a, 30, xlab = TeX(r'[$\hat{alpha}_{i}$]'),
     main = TeX(r'[Histogram of $\hat{alpha}_{i}$]'))

@@

Now, we are ready to compute the *Mean Squared Errors (MSE)* for samples used in _K-Fold Cross-Validation_ (additionally using the [clamp](#func.clamp) helper function (described in the [Utility Functions] section of [Appendix A](#appndx_a)).

>>>>

These considerations allow us to compute a _User Mean Ratings_ using the following [piece of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L231):
```{r  main-script@l1231, eval=FALSE}
put_log("Computing Average Ratings per User (User Mean Ratings)...")
user.mean_ratings <- rowMeans(edx.mx, na.rm = TRUE)
user_ratings.n <- rowSums(!is.na(edx.mx))

@@

The following [code snippet](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L336) plots a histogram that provides a visual representation of the variability of the *User Effect* across users in the *data frame object* we have just obtained:
```{r main-script@l336}
par(cex = 0.7)
hist(edx.user_effect$a, 30, xlab = TeX(r'[$\hat{alpha}_{i}$]'),
     main = TeX(r'[Histogram of $\hat{alpha}_{i}$]'))

@@

Now, we are ready to compute the *Mean Squared Errors (MSEs)* for the samples used in _K-Fold Cross-Validation_ (additionally using the [clamp](#func.clamp) helper function (described in the [Utility Functions] section of [Appendix A](#appndx_a)).

### 2025-12-23 reports/capstone-movielens.site/02.5.UME-model.Rmd
Report refactoring: references to `Appendix A`.

::: {.noteblock data-latex=""}
In the code snippet above we use the [train_user_movie_effect.cv](#func.train_user_movie_effect.cv) function described in the *Models Training: Support Functions /* [UME Model: Utility Functions] section of [Appendix A](#appndx_a).
:::

@@

::: {.noteblock data-latex=""}
In the code snippet above, we use the [calc_user_movie_effect_RMSE.cv](#func.calc_user_movie_effect_RMSE.cv) function described in the *Models Training: Support Functions /* [UME Model: Utility Functions] section of [Appendix A](#appndx_a). 
:::

@@

  - [RMSEs.AddRow](#func.RMSEs.AddRow) and [RMSE_kable](#func.RMSE_kable) (described in the *Common Helper Functions /* [Result RMSEs Tibble Functions] section) to update and print the table above.
:::

@@

::: {.noteblock data-latex=""}
The functions [tune.model_param](#func.tune.model_param) and [regularize.test_lambda.UM_effect.cv](#func.regularize.test_lambda.UM_effect.cv) are described in the sections *Common Helper Functions /* [Model Tuning Utils](#appndx_a.CHF.model_tuning_utils) and  *Models Training: Support Functions /* [UME Model: Regularization], respectively, of [Appendix A: Support Functions].
:::

@@

::: {.noteblock data-latex=""}
In the code snippet above, we use the custom data visualization function [data.plot](#func.data.plot) described in the *Data Helper Functions /* [Data Visualization Functions] section of [Appendix A](#appndx_a).
:::

@@

::: {.noteblock data-latex=""}
The helper function [get_fine_tune.param.endpoints](#func.get_fine_tune.param.endpoints) used in the code snippet above is described in the sections *Common Helper Functions /* [Model Tuning Utils](#appndx_a.CHF.model_tuning_utils) of [Appendix A: Support Functions].
:::

@@

::: {.noteblock data-latex=""}
The custom functions [model.tune.param_range](#func.model.tune.param_range) and [regularize.test_lambda.UM_effect.cv](#func.regularize.test_lambda.UM_effect.cv) used in the code snippet above are described in the sections *Common Helper Functions /* [Model Tuning Utils](#appndx_a.CHF.model_tuning_utils) and  *Models Training: Support Functions /* [UME Model: Regularization], respectively, of [Appendix A: Support Functions].
:::

@@

::: {.noteblock data-latex=""}
Note that in the code snippet above, we use the custom data visualization function [data.plot](#func.data.plot) (described in the *Data Helper Functions /* [Data Visualization Functions] section of [Appendix A](#appndx_a)) with the argument [normalize](#func.data.plot.args.normalize) set to `TRUE`, which means that deviations from the minimum $y$ value are used to plot, rather than the $y$ values themselves.
:::

@@

::: {.noteblock data-latex=""}
In the code snippet above we use the [train_user_movie_effect](#func.train_user_movie_effect) function described in the *Models Training: Support Functions /* [UME Model: Utility Functions] section of [Appendix A](#appndx_a).
:::

@@

  - [calc_user_movie_effect_RMSE.cv](#func.calc_user_movie_effect_RMSE.cv) (described in the *Models Training: Support Functions /* [UME Model: Utility Functions] section) to calculate the *RMSE* for the *UME Model*;

  - [RMSEs.AddRow](#func.RMSEs.AddRow) and [RMSE_kable](#func.RMSE_kable) (described in the *Common Helper Functions /* [Result RMSEs Tibble Functions] section) to update and print the table above.
:::

>>>>

::: {.noteblock data-latex=""}
In the code snippet above we use the [train_user_movie_effect.cv](#func.train_user_movie_effect.cv) function described in the [Models Training: Support Functions]/[UME Model: Utility Functions] section of [Appendix A](#appndx_a).
:::

@@

::: {.noteblock data-latex=""}
In the code snippet above, we use the [calc_user_movie_effect_RMSE.cv](#func.calc_user_movie_effect_RMSE.cv) function described in the [Models Training: Support Functions]/[UME Model: Utility Functions] section of [Appendix A](#appndx_a). 
:::

@@

  - [RMSEs.AddRow](#func.RMSEs.AddRow) and [RMSE_kable](#func.RMSE_kable) (described in the [Common Helper Functions]/[Result RMSEs Tibble Functions] section) to update and print the table above.
:::

@@

::: {.noteblock data-latex=""}
The functions [tune.model_param](#func.tune.model_param) and [regularize.test_lambda.UM_effect.cv](#func.regularize.test_lambda.UM_effect.cv) are described in the sections [Common Helper Functions]/[Model Tuning Utils](#appndx_a.CHF.model_tuning_utils) and  [Models Training: Support Functions]/[UME Model: Regularization], respectively, of [Appendix A: Support Functions].
:::

@@

::: {.noteblock data-latex=""}
In the code snippet above, we use the custom data visualization function [data.plot](#func.data.plot) described in the [Data Helper Functions]/[Data Visualization Functions] section of [Appendix A](#appndx_a).
:::

@@

::: {.noteblock data-latex=""}
The helper function [get_fine_tune.param.endpoints](#func.get_fine_tune.param.endpoints) used in the code snippet above is described in the sections [Common Helper Functions]/[Model Tuning Utils](#appndx_a.CHF.model_tuning_utils) of [Appendix A: Support Functions].
:::

@@

::: {.noteblock data-latex=""}
The custom functions [model.tune.param_range](#func.model.tune.param_range) and [regularize.test_lambda.UM_effect.cv](#func.regularize.test_lambda.UM_effect.cv) used in the code snippet above are described in the sections [Common Helper Functions]/[Model Tuning Utils](#appndx_a.CHF.model_tuning_utils) and  [Models Training: Support Functions]/[UME Model: Regularization], respectively, of [Appendix A: Support Functions].
:::

@@

::: {.noteblock data-latex=""}
Note that in the code snippet above, we use the custom data visualization function [data.plot](#func.data.plot) (described in the [Data Helper Functions]/[Data Visualization Functions] section of [Appendix A](#appndx_a)) with the argument [normalize](#func.data.plot.args.normalize) set to `TRUE`, which means that deviations from the minimum $y$ value are used to plot, rather than the $y$ values themselves.
:::

@@

::: {.noteblock data-latex=""}
In the code snippet above we use the [train_user_movie_effect](#func.train_user_movie_effect) function described in the [Models Training: Support Functions]/[UME Model: Utility Functions] section of [Appendix A](#appndx_a).
:::

@@

  - [calc_user_movie_effect_RMSE.cv](#func.calc_user_movie_effect_RMSE.cv) (described in the [Models Training: Support Functions]/[UME Model: Utility Functions] section) to calculate the *RMSE* for the *UME Model*;

  - [RMSEs.AddRow](#func.RMSEs.AddRow) and [RMSE_kable](#func.RMSE_kable) (described in the [Common Helper Functions]/[Result RMSEs Tibble Functions] section) to update and print the table above.
:::

### 2025-12-23 reports/capstone-movielens.site/02.6.UMGE-model.Rmd
Report refactoring: references to `Appendix A`.

::: {.noteblock data-latex=""}
In the code snippet above we use the [train_user_movie_genre_effect.cv](#func.train_user_movie_genre_effect.cv) function described in the *Models Training: Support Functions /* [UMGE Model: Utility Functions] section of [Appendix A](#appndx_a).
:::

@@

  - [calc_user_movie_genre_effect_RMSE.cv](#func.calc_user_movie_genre_effect_RMSE.cv) (described in the *Models Training: Support Functions /* [UMGE Model: Utility Functions] section) to calculate the *RMSE* for the *UMGE Model*;

  - [RMSEs.AddRow](#func.RMSEs.AddRow) and [RMSE_kable](#func.RMSE_kable) (described in the *Common Helper Functions /* [Result RMSEs Tibble Functions] section) to update and print the table above.
:::

@@

::: {.noteblock data-latex=""}
The functions [tune.model_param](#func.tune.model_param) and [regularize.test_lambda.UMG_effect.cv](#func.regularize.test_lambda.UMG_effect.cv) are described in the sections *Common Helper Functions /* [Model Tuning Utils](#appndx_a.CHF.model_tuning_utils) and  *Models Training: Support Functions /* [UMGE Model: Regularization], respectively, of [Appendix A: Support Functions].
:::

@@

::: {.noteblock data-latex=""}
The custom functions [tune.model_param](#func.tune.model_param) and [regularize.test_lambda.UMG_effect.cv](#func.regularize.test_lambda.UMG_effect.cv) used in the code snippet above are described in the sections *Common Helper Functions /* [Model Tuning Utils](#appndx_a.CHF.model_tuning_utils) and  *Models Training: Support Functions /* [UMGE Model: Regularization] of [Appendix A: Support Functions], respectively.
:::

@@

::: {.noteblock data-latex=""}
The helper function [get_fine_tune.param.endpoints](#func.get_fine_tune.param.endpoints) used in code snippet above is described in the sections *Common Helper Functions /* [Model Tuning Utils](#appndx_a.CHF.model_tuning_utils) of [Appendix A: Support Functions].
:::

@@

::: {.noteblock data-latex=""}
The custom functions [model.tune.param_range](#func.model.tune.param_range) and [regularize.test_lambda.UMG_effect.cv](#func.regularize.test_lambda.UMG_effect.cv) used in the code snippet above are described in the sections *Common Helper Functions /* [Model Tuning Utils](#appndx_a.CHF.model_tuning_utils) and  *Models Training: Support Functions /* [UMGE Model: Regularization], respectively, of [Appendix A: Support Functions].
:::

@@

::: {.noteblock data-latex=""}
In the code snippet above we use the [train_user_movie_genre_effect](#func.train_user_movie_genre_effect) function described in the *Models Training: Support Functions /* [UMGE Model: Utility Functions] section of [Appendix A](#appndx_a).
:::

>>>>

::: {.noteblock data-latex=""}
In the code snippet above we use the [train_user_movie_genre_effect.cv](#func.train_user_movie_genre_effect.cv) function described in the [Models Training: Support Functions]/[UMGE Model: Utility Functions] section of [Appendix A](#appndx_a).
:::

@@

  - [calc_user_movie_genre_effect_RMSE.cv](#func.calc_user_movie_genre_effect_RMSE.cv) (described in the [Models Training: Support Functions]/[UMGE Model: Utility Functions] section) to calculate the *RMSE* for the *UMGE Model*;

  - [RMSEs.AddRow](#func.RMSEs.AddRow) and [RMSE_kable](#func.RMSE_kable) (described in the [Common Helper Functions]/[Result RMSEs Tibble Functions] section) to update and print the table above.
:::

@@

::: {.noteblock data-latex=""}
The functions [tune.model_param](#func.tune.model_param) and [regularize.test_lambda.UMG_effect.cv](#func.regularize.test_lambda.UMG_effect.cv) are described in the sections [Common Helper Functions]/[Model Tuning Utils](#appndx_a.CHF.model_tuning_utils) and  [Models Training: Support Functions]/[UMGE Model: Regularization], respectively, of [Appendix A: Support Functions].
:::

@@

::: {.noteblock data-latex=""}
The custom functions [tune.model_param](#func.tune.model_param) and [regularize.test_lambda.UMG_effect.cv](#func.regularize.test_lambda.UMG_effect.cv) used in the code snippet above are described in the sections [Common Helper Functions]/[Model Tuning Utils](#appndx_a.CHF.model_tuning_utils) and  [Models Training: Support Functions]/[UMGE Model: Regularization] of [Appendix A: Support Functions], respectively.
:::

@@

::: {.noteblock data-latex=""}
The helper function [get_fine_tune.param.endpoints](#func.get_fine_tune.param.endpoints) used in code snippet above is described in the sections [Common Helper Functions]/[Model Tuning Utils](#appndx_a.CHF.model_tuning_utils) of [Appendix A: Support Functions].
:::

@@

::: {.noteblock data-latex=""}
The custom functions [model.tune.param_range](#func.model.tune.param_range) and [regularize.test_lambda.UMG_effect.cv](#func.regularize.test_lambda.UMG_effect.cv) used in the code snippet above are described in the sections [Common Helper Functions]/[Model Tuning Utils](#appndx_a.CHF.model_tuning_utils) and  [Models Training: Support Functions]/[UMGE Model: Regularization], respectively, of [Appendix A: Support Functions].
:::

@@

::: {.noteblock data-latex=""}
In the code snippet above we use the [train_user_movie_genre_effect](#func.train_user_movie_genre_effect) function described in the [Models Training: Support Functions]/[UMGE Model: Utility Functions] section of [Appendix A](#appndx_a).
:::

### 2025-12-23 reports/capstone-movielens.site/02.7.UMGYE-model.Rmd
Report refactoring: references to `Appendix A`.

::: {.noteblock data-latex=""}
The functions [tune.model_param](#func.tune.model_param) and [regularize.test_lambda.UMGY_effect.cv](#func.regularize.test_lambda.UMGY_effect.cv) are described in the sections *Common Helper Functions /* [Model Tuning Utils](#appndx_a.CHF.model_tuning_utils) and  *Models Training: Support Functions /* [UMGYE Model: Regularization], respectively, of [Appendix A: Support Functions].
:::

@@

::: {.noteblock data-latex=""}
The custom functions [model.tune.param_range](#func.model.tune.param_range) and [regularize.test_lambda.UMGY_effect.cv](#func.regularize.test_lambda.UMGY_effect.cv) used in the code snippet above are described in the sections *Common Helper Functions /* [Model Tuning Utils](#appndx_a.CHF.model_tuning_utils) and  *Models Training: Support Functions /* [UMGYE Model: Regularization], respectively, of [Appendix A: Support Functions].
:::

@@

::: {.noteblock data-latex=""}
In the code snippet above we use the [train_UMGY_effect](#func.train_UMGY_effect) function described in the *Models Training: Support Functions /* [UMGYE Model: Utility Functions] section of [Appendix A](#appndx_a).
:::

@@

  - [calc_UMGY_effect_RMSE.cv](#func.calc_UMGY_effect_RMSE.cv) (described in the *Models Training: Support Functions /* [UMGYE Model: Utility Functions] section) to calculate the *RMSE* for the *UMGYE Model*;

  - [RMSEs.AddRow](#func.RMSEs.AddRow) and [RMSE_kable](#func.RMSE_kable) (described in the *Common Helper Functions /* [Result RMSEs Tibble Functions] section) to update and print the table above.
:::

>>>>

::: {.noteblock data-latex=""}
The functions [tune.model_param](#func.tune.model_param) and [regularize.test_lambda.UMGY_effect.cv](#func.regularize.test_lambda.UMGY_effect.cv) are described in the sections [Common Helper Functions]/[Model Tuning Utils](#appndx_a.CHF.model_tuning_utils) and  [Models Training: Support Functions]/[UMGYE Model: Regularization], respectively, of [Appendix A: Support Functions].
:::

@@

::: {.noteblock data-latex=""}
The custom functions [model.tune.param_range](#func.model.tune.param_range) and [regularize.test_lambda.UMGY_effect.cv](#func.regularize.test_lambda.UMGY_effect.cv) used in the code snippet above are described in the sections [Common Helper Functions]/[Model Tuning Utils](#appndx_a.CHF.model_tuning_utils) and  [Models Training: Support Functions]/[UMGYE Model: Regularization], respectively, of [Appendix A: Support Functions].
:::

@@

::: {.noteblock data-latex=""}
In the code snippet above we use the [train_UMGY_effect](#func.train_UMGY_effect) function described in the [Models Training: Support Functions]/[UMGYE Model: Utility Functions] section of [Appendix A](#appndx_a).
:::

@@

  - [calc_UMGY_effect_RMSE.cv](#func.calc_UMGY_effect_RMSE.cv) (described in the [Models Training: Support Functions]/[UMGYE Model: Utility Functions] section) to calculate the *RMSE* for the *UMGYE Model*;

  - [RMSEs.AddRow](#func.RMSEs.AddRow) and [RMSE_kable](#func.RMSE_kable) (described in the [Common Helper Functions]/[Result RMSEs Tibble Functions] section) to update and print the table above.
:::

### 2025-12-23 reports/capstone-movielens.site/02.8-0.UMGYDE-model.Rmd
Report refactoring: references to `Appendix A`.

We are going to use the helper function ([train_UMGY_SmoothedDay_effect.cv](#func.train_UMGY_SmoothedDay_effect.cv) (described in section *Models Training: Support Functions /* [UMGYDE Model: Utility Functions] section of [Appendix A: Support Functions]) specifically designed to train the *UMGYDE Model*, which under the hood calls the [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) `R` function, passing its `degree` and `span` parameters values taken from the caller's [degree](#func.train_UMGY_SmoothedDay_effect.cv.args.degree) and [span](#func.train_UMGY_SmoothedDay_effect.cv.args.span) arguments, respectively.

We will start by calling the [train_UMGY_SmoothedDay_effect.cv](#func.train_UMGY_SmoothedDay_effect.cv) with default parameters, which means that the [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) function will be implicitly called with `degree = 1` and `span = 0.75` arguments - the default values for the auxiliary function [loess_de](#func.loess_de) (described in section *Models Training: Support Functions /* [UMGYDE Model: Utility Functions] section of [Appendix A](#appndx_a)) included in the call chain that actually, calls the [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) function.

@@

Let's calculate the _RMSE_ of the current model using the [calc_UMGY_SmoothedDay_effect.RMSE.cv](#func.calc_UMGY_SmoothedDay_effect.RMSE.cv) helper function described in section *Models Training: Support Functions /* [UMGYDE Model: Utility Functions] section of [Appendix A](#appndx_a):

@@

::: {.noteblock data-latex=""}
In the code snippet above we also use the [RMSEs.AddRow](#func.RMSEs.AddRow) and [RMSE_kable](#func.RMSE_kable) functions described in section *Common Helper Functions /* [Result RMSEs Tibble Functions] of [Appendix A](#appndx_a).
:::

@@

  - [tune.model_param](#func.tune.model_param) (described in the *Common Helper Functions /* [Model Tuning Utils](#appndx_a.CHF.model_tuning_utils) section) to select the best value of the *tuning parameter* (`span` in our case) from the given sequence of the *parameter values* passed in the [param_values](#func.tune.model_param.args.param_values) argument.

  - [train_UMGY_SmoothedDay_effect.RMSE.cv.degree0](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree0) (described in the *Models Training: Support Functions /* [UMGYDE Model: Tuning `loess` Params] section) used as an auxiliary function passed (in the [fn_tune.test.param_value](#func.tune.model_param.args.fn_tune.test.param_value) argument) to the [tune.model_param](#func.tune.model_param) to test the *UMGYDE Model* with the [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) `degree` parameter set to $0$.

@@

  - [model.tune.param_range](#func.model.tune.param_range) (described in the *Common Helper Functions /* [Model Tuning Utils](#appndx_a.CHF.model_tuning_utils) section) to enhance the accuracy of the *tuning parameter best value* using the *best value neighborhood* information passed in the [loop_starter](#func.model.tune.param_range.args.loop_starter) argument.

@@

::: {.noteblock data-latex=""}
In the code snippet above we use the [RMSEs.AddRow](#func.RMSEs.AddRow) and [RMSE_kable](#func.RMSE_kable) functions described in section *Common Helper Functions /* [Result RMSEs Tibble Functions] of [Appendix A](#appndx_a).
:::

@@

  - [tune.model_param](#func.tune.model_param) (described in the *Common Helper Functions /* [Model Tuning Utils](#appndx_a.CHF.model_tuning_utils) section) to select the best value of the *tuning parameter* (`span` in our case) from the given sequence of the *parameter values* passed in the [param_values](#func.tune.model_param.args.param_values) argument.

  - [train_UMGY_SmoothedDay_effect.RMSE.cv.degree1](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree1) (described in the *Models Training: Support Functions /* [UMGYDE Model: Tuning `loess` Params] section) used as an auxiliary function passed (in the [fn_tune.test.param_value](#func.tune.model_param.args.fn_tune.test.param_value) argument) to the [tune.model_param](#func.tune.model_param) to test the *UMGYDE Model* with the [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) `degree` parameter set to $1$.

@@

  - [tune.model_param](#func.tune.model_param) (described in the *Common Helper Functions /* [Model Tuning Utils](#appndx_a.CHF.model_tuning_utils) section) to select the best value of the *tuning parameter* (`span` in our case) from the given sequence of the *parameter values* passed in the [param_values](#func.tune.model_param.args.param_values) argument.

  - [train_UMGY_SmoothedDay_effect.RMSE.cv.degree2](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree2) (described in the *Models Training: Support Functions /* [UMGYDE Model: Tuning `loess` Params] section) used as an auxiliary function passed (in the [fn_tune.test.param_value](#func.tune.model_param.args.fn_tune.test.param_value) argument) to the [tune.model_param](#func.tune.model_param) to test the *UMGYDE Model* with the [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) `degree` parameter set to $2$.

@@

::: {.noteblock data-latex=""}
In the code snippet above, we use the custom data visualization function [data.plot.left_detailed](#func.data.plot.left_detailed) described in the *Data Helper Functions /* [Data Visualization Functions] section of [Appendix A](#appndx_a).
:::

@@

::: {.noteblock data-latex=""}
In the code snippet above we use the [train_UMGY_SmoothedDay_effect](#func.train_UMGY_SmoothedDay_effect) function described in the *Models Training: Support Functions /* [UMGYDE Model: Utility Functions] section of [Appendix A](#appndx_a).
:::

@@

  - [calc_UMGY_SmoothedDay_effect.RMSE.cv](#func.calc_UMGY_SmoothedDay_effect.RMSE.cv) (described in the *Models Training: Support Functions /* [UMGYDE Model: Utility Functions] section) to calculate the *RMSE* for the *UMGYDE Model*;

  - [RMSEs.AddRow](#func.RMSEs.AddRow) and [RMSE_kable](#func.RMSE_kable) (described in the *Common Helper Functions /* [Result RMSEs Tibble Functions] section) to update and print the table above.
:::

@@

::: {.noteblock data-latex=""}
The functions [tune.model_param](#func.tune.model_param) and [regularize.test_lambda.UMGYD_effect.cv](#func.regularize.test_lambda.UMGYD_effect.cv) are described in the sections *Common Helper Functions /* [Model Tuning Utils](#appndx_a.CHF.model_tuning_utils) and  *Models Training: Support Functions /* [UMGYE Model: Regularization], respectively, of [Appendix A: Support Functions].
:::

@@

::: {.noteblock data-latex=""}
The custom functions [model.tune.param_range](#func.model.tune.param_range) and [regularize.test_lambda.UMGYD_effect.cv](#func.regularize.test_lambda.UMGYD_effect.cv) used in the code snippet above are described in the sections *Common Helper Functions /* [Model Tuning Utils](#appndx_a.CHF.model_tuning_utils) and  *Models Training: Support Functions /* [UMGYE Model: Regularization], respectively, of [Appendix A: Support Functions].
:::

@@

::: {.noteblock data-latex=""}
In the code snippet above we use the [regularize.train_UMGYD_effect](#func.regularize.train_UMGYD_effect) function described in the *Models Training: Support Functions /* [UMGYDE Model: Regularization] section of [Appendix A](#appndx_a).
:::

>>>>

We are going to use the helper function ([train_UMGY_SmoothedDay_effect.cv](#func.train_UMGY_SmoothedDay_effect.cv) (described in section [Models Training: Support Functions]/[UMGYDE Model: Utility Functions] section of [Appendix A: Support Functions]) specifically designed to train the *UMGYDE Model*, which under the hood calls the [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) `R` function, passing its `degree` and `span` parameters values taken from the caller's [degree](#func.train_UMGY_SmoothedDay_effect.cv.args.degree) and [span](#func.train_UMGY_SmoothedDay_effect.cv.args.span) arguments, respectively.

We will start by calling the [train_UMGY_SmoothedDay_effect.cv](#func.train_UMGY_SmoothedDay_effect.cv) with default parameters, which means that the [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) function will be implicitly called with `degree = 1` and `span = 0.75` arguments - the default values for the auxiliary function [loess_de](#func.loess_de) (described in section [Models Training: Support Functions]/[UMGYDE Model: Utility Functions] section of [Appendix A](#appndx_a)) included in the call chain that actually, calls the [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) function.

@@

Let's calculate the _RMSE_ of the current model using the [calc_UMGY_SmoothedDay_effect.RMSE.cv](#func.calc_UMGY_SmoothedDay_effect.RMSE.cv) helper function described in section [Models Training: Support Functions]/[UMGYDE Model: Utility Functions] section of [Appendix A](#appndx_a):

@@

::: {.noteblock data-latex=""}
In the code snippet above we also use the [RMSEs.AddRow](#func.RMSEs.AddRow) and [RMSE_kable](#func.RMSE_kable) functions described in section [Common Helper Functions]/[Result RMSEs Tibble Functions] of [Appendix A](#appndx_a).
:::

@@

  - [tune.model_param](#func.tune.model_param) (described in the [Common Helper Functions]/[Model Tuning Utils](#appndx_a.CHF.model_tuning_utils) section) to select the best value of the *tuning parameter* (`span` in our case) from the given sequence of the *parameter values* passed in the [param_values](#func.tune.model_param.args.param_values) argument.

  - [train_UMGY_SmoothedDay_effect.RMSE.cv.degree0](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree0) (described in the [Models Training: Support Functions]/[UMGYDE Model: Tuning `loess` Params] section) used as an auxiliary function passed (in the [fn_tune.test.param_value](#func.tune.model_param.args.fn_tune.test.param_value) argument) to the [tune.model_param](#func.tune.model_param) to test the *UMGYDE Model* with the [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) `degree` parameter set to $0$.

@@

  - [model.tune.param_range](#func.model.tune.param_range) (described in the [Common Helper Functions]/[Model Tuning Utils](#appndx_a.CHF.model_tuning_utils) section) to enhance the accuracy of the *tuning parameter best value* using the *best value neighborhood* information passed in the [loop_starter](#func.model.tune.param_range.args.loop_starter) argument.

@@

::: {.noteblock data-latex=""}
In the code snippet above we use the [RMSEs.AddRow](#func.RMSEs.AddRow) and [RMSE_kable](#func.RMSE_kable) functions described in section [Common Helper Functions]/[Result RMSEs Tibble Functions] of [Appendix A](#appndx_a).
:::

@@

  - [tune.model_param](#func.tune.model_param) (described in the [Common Helper Functions]/[Model Tuning Utils](#appndx_a.CHF.model_tuning_utils) section) to select the best value of the *tuning parameter* (`span` in our case) from the given sequence of the *parameter values* passed in the [param_values](#func.tune.model_param.args.param_values) argument.

  - [train_UMGY_SmoothedDay_effect.RMSE.cv.degree1](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree1) (described in the [Models Training: Support Functions]/[UMGYDE Model: Tuning `loess` Params] section) used as an auxiliary function passed (in the [fn_tune.test.param_value](#func.tune.model_param.args.fn_tune.test.param_value) argument) to the [tune.model_param](#func.tune.model_param) to test the *UMGYDE Model* with the [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) `degree` parameter set to $1$.

@@

  - [tune.model_param](#func.tune.model_param) (described in the [Common Helper Functions]/[Model Tuning Utils](#appndx_a.CHF.model_tuning_utils) section) to select the best value of the *tuning parameter* (`span` in our case) from the given sequence of the *parameter values* passed in the [param_values](#func.tune.model_param.args.param_values) argument.

  - [train_UMGY_SmoothedDay_effect.RMSE.cv.degree2](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree2) (described in the [Models Training: Support Functions]/[UMGYDE Model: Tuning `loess` Params] section) used as an auxiliary function passed (in the [fn_tune.test.param_value](#func.tune.model_param.args.fn_tune.test.param_value) argument) to the [tune.model_param](#func.tune.model_param) to test the *UMGYDE Model* with the [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) `degree` parameter set to $2$.

@@

::: {.noteblock data-latex=""}
In the code snippet above, we use the custom data visualization function [data.plot.left_detailed](#func.data.plot.left_detailed) described in the [Data Helper Functions]/[Data Visualization Functions] section of [Appendix A](#appndx_a).
:::

@@

::: {.noteblock data-latex=""}
In the code snippet above we use the [train_UMGY_SmoothedDay_effect](#func.train_UMGY_SmoothedDay_effect) function described in the [Models Training: Support Functions]/[UMGYDE Model: Utility Functions] section of [Appendix A](#appndx_a).
:::

@@

  - [calc_UMGY_SmoothedDay_effect.RMSE.cv](#func.calc_UMGY_SmoothedDay_effect.RMSE.cv) (described in the [Models Training: Support Functions]/[UMGYDE Model: Utility Functions] section) to calculate the *RMSE* for the *UMGYDE Model*;

  - [RMSEs.AddRow](#func.RMSEs.AddRow) and [RMSE_kable](#func.RMSE_kable) (described in the [Common Helper Functions]/[Result RMSEs Tibble Functions] section) to update and print the table above.
:::

@@

::: {.noteblock data-latex=""}
The functions [tune.model_param](#func.tune.model_param) and [regularize.test_lambda.UMGYD_effect.cv](#func.regularize.test_lambda.UMGYD_effect.cv) are described in the sections [Common Helper Functions]/[Model Tuning Utils](#appndx_a.CHF.model_tuning_utils) and  [Models Training: Support Functions]/[UMGYE Model: Regularization], respectively, of [Appendix A: Support Functions].
:::

@@

::: {.noteblock data-latex=""}
The custom functions [model.tune.param_range](#func.model.tune.param_range) and [regularize.test_lambda.UMGYD_effect.cv](#func.regularize.test_lambda.UMGYD_effect.cv) used in the code snippet above are described in the sections [Common Helper Functions]/[Model Tuning Utils](#appndx_a.CHF.model_tuning_utils) and  [Models Training: Support Functions]/[UMGYE Model: Regularization], respectively, of [Appendix A: Support Functions].
:::

@@

::: {.noteblock data-latex=""}
In the code snippet above we use the [regularize.train_UMGYD_effect](#func.regularize.train_UMGYD_effect) function described in the [Models Training: Support Functions]/[UMGYDE Model: Regularization] section of [Appendix A](#appndx_a).
:::
